Building the Torus Radiative Transfer Code

### 2009-06-02 torus/docs/how_to_build_torus.tex
Replace image_f77.f files and spec_f77.f files with F90 versions which use the USENDF cpp key to control whether NDF support is enabled. It is no longer necessary to specify whether NDF support is enabled when defining the SYSTEM in the Makefile. The default behaviour is not to use NDF but this can be changed by using make ndf=yes.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@1932 25464f21-6099-402c-b30a-640f1d40d38b

\begin{table}
  \begin{center}
    \begin{tabular}[|l|l|l|]{|l|l|l|}
\hline
    Option    & Description & Default \\
\hline
      cfitsio & link with cfitsio libraries & yes \\
      debug   & switch on debugging flags   & no  \\
      profile & enable profiling            & no  \\
      static  & perform static linking      & no  \\
      trace   & use Intel trace collector   & no  \\
\hline
  \end{tabular}
\caption{Options which can be supplied to the make command when
  building torus.}
\label{table:make_options}
\end{center}
\end{table}

>>>>

\begin{table}
  \begin{center}
    \begin{tabular}[|l|l|l|]{|l|l|l|}
\hline
    Option    & Description & Default \\
\hline
      cfitsio & link with cfitsio libraries & yes \\
      ndf & build with NDF file support & no \\
      debug   & switch on debugging flags   & no  \\
      profile & enable profiling            & no  \\
      static  & perform static linking      & no  \\
      trace   & use Intel trace collector   & no  \\
\hline
  \end{tabular}
\caption{Options which can be supplied to the make command when
  building torus.}
\label{table:make_options}
\end{center}
\end{table}
